Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-08-17 theory/sec_08.tex
Theory corrections manipulate conductivity

Now using the relations derived in Eq. \eqref{5.34} and Eq. \eqref{7.17} we can derive that
\begin{equation} \label{8.1}
  \Gamma_n = \qty(\frac{\hbar }{2\tau(\varepsilon_n)}) =
  \frac{1}{2}\Gamma^{00}_{N}(\tilde{I})
\end{equation}
and this will be
\begin{equation} \label{8.2}
  \Gamma_n(\tilde{I}) = 0.12\times
  \qty[
  \frac
  {\int_{-\infty}^{\infty} d {k}_1 \;
  J_0^2\qty(2.090\sqrt{\tilde{I}}\times{k}_1)
  \qty|
  \int_{-\infty}^{\infty} d{k}_2 \;
  \tilde{\chi}_{N}\qty(2.342 \times k_2)
  \tilde{\chi}_{N}\qty(2.342 \times \qty[{k}_1 - {k}_2])|^2}
  {\int_{-\infty}^{\infty} d {k}_1 \;
  \qty|
  \int_{-\infty}^{\infty} d{k}_2 \;
  \tilde{\chi}_{0}\qty(2.342 \times k_2)
  \tilde{\chi}_{0}\qty(2.342 \times \qty[{k}_1 - {k}_2])|^2}
  ]^{1/2} \text{meV}
\end{equation}

>>>>

Now using the relations derived in Eq. \eqref{5.34} and Eq. \eqref{7.17} we can derive that
\begin{equation} \label{8.1}
  \Gamma_n = \qty(\frac{\hbar }{2\tau(\varepsilon_n)}) =
  \frac{1}{2}\Gamma^{00}_{N}(\tilde{I}),
\end{equation}
and using \eqref{5.32}, this can be re-write as follows
\begin{equation} \label{8.2}
   \Gamma_n = \frac{1}{2} \Lambda_N (\tilde{I}) \Gamma^{00}_{N=0}\big|_{E=0}.
\end{equation}
Let $\Gamma^{00}_{N=0}\big|_{E=0} = \Gamma_0$ and this leads to
\begin{equation} \label{8.3}
   \gamma_n = \frac{\Gamma_n}{\hbar \omega_0} =
   \frac{\Gamma_0}{2\hbar \omega_0} \Lambda_N (\tilde{I})
\end{equation}
Let $\alpha \equiv \flatfrac{\Gamma_0}{2\hbar \omega_0}$ and we can obtain
\begin{equation} \label{8.4}
   \gamma_n = \alpha \Lambda_N (\tilde{I})
\end{equation}
Thus we can write the transverse conductivity as a function of fermi energy and intensity
\begin{equation} \label{8.5}
  \begin{aligned}
    \sigma^{xx}(X_F,\tilde{I}) & =
    \frac{e^2}{\pi\hbar A}
    \sum_{n}
    \frac{\qty(n+1)}{\alpha^2 \Lambda_n \Lambda_{n+1}}
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n -1}{\alpha\Lambda_n})^2
      }
    ]
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n}{\alpha\Lambda_{n+1}})^2
      }
    ].
  \end{aligned}
\end{equation}
Then we can define a normalized transverse conductivity as follows
\begin{equation} \label{8.6}
  \begin{aligned}
    \widetilde{\sigma}^{xx}(X_F,\tilde{I}) =
    \flatfrac{\sigma^{xx}}{\sigma_0} =
    \sum_{n}
    \frac{\qty(n+1)}{\alpha^2 \Lambda_n \Lambda_{n+1}}
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n -1}{\alpha\Lambda_n})^2
      }
    ]
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n}{\alpha\Lambda_{n+1}})^2
      }
    ],
  \end{aligned}
\end{equation}
where $\sigma_0 = \flatfrac{e^2}{(\pi\hbar A)}$.

Above parameters can be evaluated for our experiment variables($\Gamma_0 = 0.24 \text{meV}$) as follows
\begin{equation} \label{8.2}
  \Gamma_n(\tilde{I}) = 0.12\times
  \qty[
  \frac
  {\int_{-\infty}^{\infty} d {k}_1 \;
  J_0^2\qty(2.090\sqrt{\tilde{I}}\times{k}_1)
  \qty|
  \int_{-\infty}^{\infty} d{k}_2 \;
  \tilde{\chi}_{N}\qty(2.342 \times k_2)
  \tilde{\chi}_{N}\qty(2.342 \times \qty[{k}_1 - {k}_2])|^2}
  {\int_{-\infty}^{\infty} d {k}_1 \;
  \qty|
  \int_{-\infty}^{\infty} d{k}_2 \;
  \tilde{\chi}_{0}\qty(2.342 \times k_2)
  \tilde{\chi}_{0}\qty(2.342 \times \qty[{k}_1 - {k}_2])|^2}
  ]^{1/2} \text{meV}
\end{equation}
